### 2024-01-31 revision/reply_to_reviewer1.tex

\referee{The PSF approximation in this paper is built for more general
  operators than Hessian. It demonstrates the effectiveness of the
  PSF-based method by 1 using it to build preconditioners for the
  Hessian operator in two challenging inverse problems of basal
  friction coefficient inversion of ice sheet flow and ini- tial
  condition inversion of advection-dominated transport. It shows
  significant reductions (5-10X) in the required number of PDE solves
  compared to classical regularization-based preconditioning and no
  preconditioning. The paper also presents a comprehensive numerical
  study on the influence of various parameters (data noises, \# batchs,
  diffusion coefficients, terminal times) on the effective- ness and
  data-scalability of the proposed method, showing that the PSF-based
  preconditioners can form good approximations of high-rank Hessians
  using only a small number of operator applications.  The proposed
  method is very interesting and makes a great contribution to solving
  large-scale inverse problems with high-rank Hessians. The
  presentation of the proposed method is concise and illustrative. The
  numerical results are very convincing. Overall, the paper is very
  well written.\\}

\noindent{Thank you for the positive assesment of our work.\\}

@@

\paragraph{General Comments:}

\referee{I recommend to accept the paper for publication with minor
  revisions. I suggest the authors properly address the following
  questions to help for its better understanding and broader
  applications.\\}

\begin{enumerate} 
\item \referee{The author mentioned one limitation of the proposed method:
      the Hessian should have a local non-negative integral kernel,
      which is not satisfied for wave inverse problems that lead to a
      substantial amount of negative entries of the Hessian. It would
      be interesting if the author could elaborate more details with
      intuition or numerical evidence for this property and the
      limitation, especially if you also use Gauss-Newton approximate
      Hessian for the wave inverse problems as in this paper.}

\noindent{(1) Three-figure plot: Stokes, Advection/diffusion, wave impulse responses.

(2) showing that the method performs poorly for the ricker example

Nick will try to get an impulse response for the wave
  problem.}

@@

\item \referee{It is interesting to see the effectiveness of the
  approximate Hessian used as a preconditioner. It would also be very
  interesting to see how accurate the approximate Hessian is compared
  to a full Hessian in terms of the number of batches, ellipsoid
  sizes, and in particular the total number of impulse responses. Can
  you say anything about the convergence of the approximation, either
  numerical or theoretical?}

  \noindent{
  	Frog example with a=1. Error vs #batches, for different tau. Also do a plot with #impulses on the x-axis.

  	Nick will try to create a plot that shows some error
    (e.g. Frob norm, cond number) as a function of number of impulse
    responses.}

### 2024-01-31 revision/reply_to_reviewer2.tex

Thanks for the careful reading and for your helpful comments and
suggestions.  Please find below point-by-point replies (in black) to
your comments and questions (which are reprinted in blue). To give you
an overview of all the changes in the paper, we also provide a
diff-document that highlights the changes between the initial
submission and this re-submission.\\[1ex]

\referee{I have read the paper with pleasure and have the following
  suggestions for improvement:\\}

\begin{enumerate}
\item \referee{Interesting work, generally well-written. Perhaps a
  small illustrative example with a few figures at the beginning could
  help understand the procedure intuitively.}

  \noindent{Frog example with a=1.
  	Structure: local non-negative kernel
(0) Matrix itself column highlighted, show impulse response
(1) moments. Show one impulse with ellipsoid with widths illustrated
(2) impulse response batches
(3) RBF interpolation (?)
(4) H-matrix
}

@@

\item \referee{possibly interesting references for estimating Hessians
  in linearised seismic imaging include:
  \url{https://doi.org/10.1016/j.acha.2007.06.007},
  \url{https://doi.org/10.1190/1.2836323}}

  \noindent{We added text in the paragraph at the end of Section 2 to discuss the (lack of) applicability of the method to wave inverse problems and added these references.}

### 2024-02-05 revision/reply_to_reviewer2.tex

Thanks for the careful reading and for your helpful comments and
suggestions.  Please find below point-by-point replies (in black) to
your comments and questions (which are reprinted in blue). To give you
an overview of all the changes in the paper, we also provide a
diff-document that highlights the changes between the initial
submission and this re-submission.\\[1ex]

\referee{I have read the paper with pleasure and have the following
  suggestions for improvement:\\}

\begin{enumerate}
\item \referee{Interesting work, generally well-written. Perhaps a
  small illustrative example with a few figures at the beginning could
  help understand the procedure intuitively.}

  \noindent{Frog example with a=1.
  	Structure: local non-negative kernel
(0) Matrix itself column highlighted, show impulse response
(1) moments. Show one impulse with ellipsoid with widths illustrated
(2) impulse response batches
(3) RBF interpolation (?), evaluation of entries. Columns we know, and entry we don't know. 
(4) H-matrix
}

### 2024-02-09 paper_sisc_first_revision/localpsf.tex
blur example working ok
unclear how to illustrate h-matrix stuff
put more frog example images into paper
finished draft of interpolation figure
update illustrations
generated columnwise error plots and added to paper

@@

\section*{Acknowledgments}
We thank J.J. Alger, Longfei Gao, Mathew Hu, and Rami Nammour for helpful discussions. We thank Trevor Heise for editing suggestions. We thank Georg Stadler for help with the domain setup for the ice sheet problem.

>>>>

\section{Illustration of the method on a spatially variant blur operator}

Before delving into technical details, we illustrate the method on a spatially variant blurring operator with the following integral kernel:
$$\Phi(y,x) = (1 - a f(y,x)) g(x) \exp \left(-\frac{1}{2}h^T(y,x) C^{-1} h(y,x)\right).$$ 
Here, $h(y,x) = R(\theta(x)) (y-x)$, $R(\theta(x))$ is the 2D rotation matrix by angle $\theta(x) = (x^1 + x^2) \pi / 2$, $C = L^2 \operatorname{diag}(c_1, c_2)$, $g(x) = x^1(1-x^1)x^2(1-x^2)$,  and $f(x,y) = \cos\left(p^1(y,x) / \sqrt{c_1 / 2.0}\right) \sin\left(p^2(y,x) / \sqrt{c_2 / 2.0}\right)$ for some constants $a, L, c_1, c_2$. We use $a=1.0$, $L^2=1.0$, $c_1=0.01$, and $c_2=0.0025$. Using this kernel, the impulse responses, $\phi_x$, are bumpy blobs that are centered roughly at $x$, and are rotated and scaled in a manner that depends on $x$ (see Figure \ref{fig:frog1}). The constant $L$ controls how wide the blob is, and $a$ controls the bumpiness. With $a=0$, $\phi_x$ is a Gaussian. As $a$ increases, $\phi_x$ becomes more bumpy. When $a > 1$, the integral kernel contains negative values, which violates the assumptions of our method. In the numerical results section we will vary $a$ and $L$, even allowing $a>1$ to test the robustness of the method to violations of the non-negative kernel assumption. Note that for this operator, using our method is unnecessary because entries of the kernel are given directly via a formula. The purpose of this example is to illustrate and test the method on an operator which is known exactly and may be easily visualized.

\begin{figure}
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[scale=0.25]{kernel_impulse_illustration2.pdf}
		\caption{Kernel and impulse responses}
		\label{fig:kernel_impulse_illustration}
	\end{subfigure}
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[scale=0.5]{frog_ellipsoid_width.pdf}
		\caption{Impulse response support ellipsoid}
		\label{fig:frog_ellipsoid_width}
	\end{subfigure}

	\caption{(\ref{fig:kernel_impulse_illustration}) asdf. \ref{fig:frog_ellipsoid_width}) asdf2
	}
	\label{fig:frog1}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[scale=0.25]{frog_moments2.pdf}	
	\caption{asdf3
	}
	\label{fig:frog2}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[scale=0.3]{frog_batches2.pdf}	
	\caption{asdf4
	}
	\label{fig:frog3}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[scale=0.24]{frog_hmatrix_knn_impulse2.png}	
	\caption{asdfg
	}
	\label{fig:frog4}
\end{figure}

\begin{figure}
	\begin{subfigure}[b]{0.30\textwidth}
		\centering
		\includegraphics[scale=0.4]{frog_column_errors_psf5.png}
		\caption{PSF(5)}
		\label{fig:blur_error_psf5}
	\end{subfigure}
	\begin{subfigure}[b]{0.30\textwidth}
		\centering
		\includegraphics[scale=0.4]{frog_column_errors_psf10.png}
		\caption{PSF(10)}
		\label{fig:blur_error_psf10}
	\end{subfigure}
	\begin{subfigure}[b]{0.38\textwidth}
		\centering
		\includegraphics[scale=0.4]{frog_column_errors_psf20_colorbar.png}
		\caption{PSF(20)}
		\label{fig:blur_error_psf20}
	\end{subfigure}

	\caption{columnwise error plots for kernel reconstruction
	}
	\label{fig:frog5}
\end{figure}

@@

\section*{Acknowledgments}
We thank J.J. Alger, Longfei Gao, Mathew Hu, and Rami Nammour for helpful discussions. The seismic Hessian impulse response image was provided to us by Mathew Hu. We thank Trevor Heise for editing suggestions. We thank Georg Stadler for help with the domain setup for the ice sheet problem.
